\input{ main-style }

\title{Assignment P5\\}

\authoremail{Jeremy Martinez}{jmartinez91@gmail.com}

\begin{document}
\maketitle
\thispagestyle{fancy}

\section{Question 1}
First, select and describe a specific positive effect of the existence of programs like Georgia Tech’s OMSCS,
  emphasizing how that positive effect is due to specific elements of the program
  (such as its low cost, its asynchronous structure, its subsidized model, etc.).

Then, select a potential negative repercussion of programs like Georgia Tech’s OMSCS,
  emphasizing how that negative effect is also due to specific elements of the program.

Finally, design how the program can be structured to preserve the positive effect while limiting the negative effect.

\section{Question 2}

Identify an area you encounter regularly where political motivations are determining the design of technology.
  First, describe the area you’ve selected.

Then, describe the stakeholders in that area, including their motivations.
  Any interesting technology will likely have at least three groups of stakeholders.

Then, describe at least three ways those motivations are specifically affecting the design of the technology in that area.
  If you’re on the right track, you’ll likely find the motivations are in conflict.

\section{Question 3}

Every year, ACM CHI is the world’s largest conference on Human-Computer Interaction.
  Select two papers from one of the most recent three CHI conferences (2019, 2018, 2017).
  For each of the two papers, list the paper’s title and author list, and then briefly summarize the paper.
  In summarizing, be careful not to restate the abstract:
    the abstract for the paper emphasizes the paper’s significance,
    but your summary should focus on describing the paper to someone unfamiliar with the contents at all.

Then, describe why you find this paper interesting or why you selected it for this assignment.

\section{Question 4}

Select two different conferences from this list. <see list in assignment description>
  Then, from each conference, select a paper.
  For each of the two papers, list the paper’s title and author list, and then briefly summarize the paper.
  In summarizing, be careful not to restate the abstract:
    the abstract for the paper emphasizes the paper’s significance,
    but your summary should focus on describing the paper to someone unfamiliar with the contents at all.

Then, describe why you find this paper interesting or why you selected it for this assignment.

\end{document}
