\begin{itemize}
\item Home page
  \begin{itemize}
  \item Homepage is very aesthetic, and the picture gives me a sense of a good road trip already
  \item "Let's get started" is taking me (immediately) to what I need
  \end{itemize}
\item Maps page
  \begin{itemize}
  \item "You trip is not saved" suggests I can create an account and return to this (so I don't have to do it all at once)
  \item Also, some friends and I could create a joint account and edit the same trip! I wonder if they can create their own account and I can share the trip with them?
  \item The map looks and feels a little bit like Google Maps
  \item "Scenic" map option seems to be paid for...
    \begin{itemize}
    \item What are "waypoints"? (one perk of paid option)
    \item Ah, trip collaboration, (answer to question from earlier)
    \item Offline maps, live traffic would be useful, but I can just use Google Maps for that... (had to remind user that this is not for navigation, but trip planning only)
    \end{itemize}
  \item Bar on left gives me options for what I'm looking for, attractions, places to sleep, etc.
  \item Clicking "get help" did nothing...
  \item The route defaults to the I-5 option that I was told I couldn't take
  \item But, the route seems draggable, so I can just move the route over to highway 1
  \item I don't recognize the check points along the path, but it is nice how I get a time breakdown between them all.
  \end{itemize}
\item Route metrics
  \begin{itemize}
  \item I think I've got the route figured out now.
  \item The overall distance of the trip is 461 miles.
  \item The over driving time of the trip is 9:39
  \end{itemize}
\item Finding accommodation
  \begin{itemize}
  \item The check points break down as
    \begin{itemize}
    \item 1) 0:00 (San Fran)
    \item 2) 1:12
    \item 3) 2:06
    \item 4) 0:57
    \item 5) 3:02
    \item 6) 2:23
    \end{itemize}
  \item I'm still not sure why these are my "waypoints." It's also telling me I only get 1 "waypoint" left. Why's that?
  \item Since the half way point (time-wise) is between 4-5, I will find accommodation here. Clicking the bed icon seems to give me options. This is clear and intuitive since this icon could only mean that one thing
  \item I really like the dollar sign slide bar, easy to find cheap places to stay!
  \item Motel 6's are gross (HA!)
  \item We will stay at Treebones Resort (seems about half way), only two dollar signs (not really sure if that's cheap or not). Maybe some indication to what dollar amount that means would be nice...
  \item Clicked this and it took me to a different page... clicking add to trip. It says it has no availability for any dates I select... this is discouraging
  \end{itemize}
\item I'm out of free "waypoints"... looks like I can't add anything more in this tool (instructing them to use a pen and paper from here on out)
\item Running out of "waypoints" makes it feel like they are nickle and dime-ing me.. kind of frustrating since it has not demonstrated enough value for me to want to pay for it. I can't actually complete the task with adding all my stops unless I pay for this service...
\item Finding attractions
  \begin{itemize}
  \item There are way too many attractions to sift through, feels overwhelming.
  \item Reading through these attractions, a lot of these sound boring.. I don't care about most of these.
  \item There's a small green number in the upper left of the image, 1-5 it seems
  \item World's largest artichoke, HA! The surfing museum might be cool
  \item The beaches filter is good, we will add the highest rated beach to our list
  \item Cowell Ranch beach looks very cool too! We will stop there (1)
  \item Now I am scrolling past anything with less than 4.5 rating!
  \item We'll go to one of the vineyards near our destination for dinner night 1, August Ridge Vineyards (1)
  \item I wish there were filters for attractions
  \item I like the profile pages of the attractions, but why don't they just show Google reviews? I have to separately google everything. When I googled something with a 5.0 rating, the Google search result said it was permanently closed... I'm definitely not paying for this service
  \item Fly above all paragliding for the last attraction! (2)
  \item Santa Barbara brewing co is near here, we'll have that as our second planned meal (2)
  \end{itemize}
\item Emailed the link to myself to save it. I would also create an account so that it just saves to that and I can log in later for it
\end{itemize}
